---
title: "HW6 Ep2899"
output: github_document
---

```{r setup, include=FALSE}

library(tidyverse)
library(viridis)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

theme_set(theme_minimal() + theme(legend.position = "bottom"))
```

```{r load_libraries}
library(tidyverse)
library(modelr)
library(p8105.datasets)
library(mgcv)
```

## Problem 1

Read in the data.
```{r}
homicide_df = 
  read_csv("data/homicide-data.csv", na = c("", "NA", "Unknown")) %>% 
  mutate(
    city_state = str_c(city, state, sep = ", "),
    victim_age = as.numeric(victim_age),
    resolution = case_when(
      disposition == "Closed without arrest" ~ 0,
      disposition == "Open/No arrest"        ~ 0,
      disposition == "Closed by arrest"      ~ 1)
  ) %>% 
  filter(
    victim_race %in% c("White", "Black"),
    city_state != "Tulsa, AL") %>% 
  select(city_state, resolution, victim_age, victim_race, victim_sex)
```
Start with one city.

```{r}
baltimore_df =
  homicide_df %>% 
  filter(city_state == "Baltimore, MD")

glm(resolution ~ victim_age + victim_race + victim_sex, 
    data = baltimore_df,
    family = binomial()) %>% 
  broom::tidy() %>% 
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  select(term, OR, starts_with("CI")) %>% 
  knitr::kable(digits = 3)
```


Try this across cities.

```{r}
models_results_df = 
  homicide_df %>% 
  nest(data = -city_state) %>% 
  mutate(
    models = 
      map(.x = data, ~glm(resolution ~ victim_age + victim_race + victim_sex, data = .x, family = binomial())),
    results = map(models, broom::tidy)
  ) %>% 
  select(city_state, results) %>% 
  unnest(results) %>% 
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  select(city_state, term, OR, starts_with("CI")) 
```

```{r}
models_results_df %>% 
  filter(term == "victim_sexMale") %>% 
  mutate(city_state = fct_reorder(city_state, OR)) %>% 
  ggplot(aes(x = city_state, y = OR)) + 
  geom_point() + 
  geom_errorbar(aes(ymin = CI_lower, ymax = CI_upper)) + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

## Problem 2
Load and clean the data for regression analysis (i.e. convert numeric to factor where appropriate, check for missing data, etc
```{r}
baby_df=
  read_csv("./data/birthweight.csv")
```

Propose a regression model for birthweight. This model may be based on a hypothesized structure for the factors that underly birthweight, on a data-driven model-building process, or a combination of the two. Describe your modeling process and show a plot of model residuals against fitted values 
```{r}
baby_df %>% 
  ggplot(aes(x = delwt, y = bwt)) + 
  geom_point()


baby_df %>% 
    mutate(
    mrace = as.factor(mrace),
    babysex = as.factor(babysex),
    malform = as.factor(malform)
  )

model_fit = lm (bwt ~babysex+delwt+gaweeks+malform+momage+mrace+pnumlbw+ppbmi+ppwt+smoken+wtgain, data = baby_df)
```

```{r, include = FALSE}
model_fit

summary(model_fit)
summary(model_fit)$coef 
coef(model_fit)
residuals(model_fit)
```

```{r}
broom::glance(model_fit)

broom::tidy(model_fit) 
```


```{r}
baby_df %>% 
  modelr::add_residuals (model_fit) %>% 
  ggplot (aes (x = resid)) +
  geom_density ()
```

```{r}
baby_df %>% 
  add_predictions(model_fit) %>% 
  ggplot(aes(x = pred)) + 
  geom_density()
```

One using length at birth and gestational age as predictors (main effects only)
```{r}
model_fit2 = lm (bwt ~ blength+gaweeks, data = baby_df)
```

One using head circumference, length, sex, and all interactions (including the three-way interaction) between these
```{r}
model_fit3 = lm (bwt ~ blength + bhead + babysex + blength*bhead + bhead*babysex +blength*babysex + blength*bhead*babysex, data = baby_df)
```

Make this comparison in terms of the cross-validated prediction error; use crossv_mc and functions in purrr as appropriate
```{r}
baby_df %>% 
  gather_predictions(model_fit, model_fit2, model_fit3) %>% 
  ggplot(aes(x = babysex+delwt+gaweeks+malform+momage+mrace+pnumlbw+ppbmi+ppwt+smoken+wtgain, y = bwt)) +
  geom_point(alpha = .3) +
  geom_line(aes(y = pred), color = "red") + 
  facet_grid(. ~ model)
```

```{r}
cvbaby_df = 
  crossv_mc(baby_df, 100) %>% 
    mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble)
  )
```


```{r}
  cvbaby_df %>% 
  mutate(
    model_fit = map(.x = train, ~lm(bwt ~babysex+delwt+gaweeks+malform+momage+mrace+pnumlbw+ppbmi+ppwt+smoken+wtgain, data = .x)),
    model_fit2 = map(.x = train, ~ lm(bwt ~ blength+gaweeks, data = .x)),
    model_fit3 = map(.x = train, ~ lm(bwt ~ blength + bhead + babysex + blength*bhead + bhead*babysex +blength*babysex + blength*bhead*babysex, data = .x))
  ) %>% 
  mutate(
    rmse_model_fit = map2_dbl(.x = model_fit, .y = test, ~rmse(model = .x, data = .y)),
    rmse_model_fit2 = map2_dbl(.x = model_fit2, .y = test, ~rmse(model = .x, data = .y)),
    rmse_model_fit3 = map2_dbl(.x = model_fit3, .y = test, ~rmse(model = .x, data = .y))
  )
```

## Problem 3
```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

The bootstrap is helpful when you’d like to perform inference for a parameter / value / summary that doesn’t have an easy-to-write-down distribution in the usual repeated sampling framework. We’ll focus on a simple linear regression with tmax as the response and tmin as the predictor, and are interested in the distribution of two quantities estimated from these data: r^2 and log(β^0∗β^1)

fit a model to weather_df

```{r}
weather_fit = lm (tmax ~tmin, data = weather_df)
```


```{r, include = FALSE}
weather_fit

summary(weather_fit)
summary(weather_fit)$coef 
coef(weather_fit)
residuals(weather_fit)
```

Use 5000 bootstrap samples and, for each bootstrap sample, produce estimates of these two quantities. Plot the distribution of your estimates, and describe these in words.
```{r}
weather_fit %>% 
broom::tidy()
```


```{r}
boot_sample = function(weather_df) {
  
  sample_frac(weather_df, replace = TRUE) %>% 
    arrange(x)
  
}
```


Using the 5000 bootstrap estimates, identify the 2.5% and 97.5% quantiles to provide a 95% confidence interval for r^2 and log(β^0∗β^1). 
```{r}
weatherdf_boot_results = 
  weather_df %>% 
  bootstrap(5000, id = "strap_number") %>% 
  mutate(
   models = map(strap, ~ lm(tmax ~tmin, data = weather_df)),
    results = map(models, broom::tidy)
   ) %>% 
  select(results) %>% 
  unnest(results) 

weatherdf_boot_results %>% 
  group_by(term) %>% 
  summarize(
    mean_est = mean(estimate),
    sd_est = sd(estimate)
  )
```

```{r}
weatherdf_boot_results %>%
  group_by(term) %>% 
  summarize(
    ci_lower = quantile(estimate, 0.025),
    ci_upper = quantile(estimate, 0.975)
  )
```